```{r}
setwd("G:\\Projects\\R\\Reproducible\\RepData_PeerAssessment1")
```

# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r, echo=TRUE}
dataFile <- read.csv("activity2.csv")
dataFile$date <- as.Date(dataFile$date, format="%d/%m/%Y")
```

## What is mean total number of steps taken per day?
```{r mm}
d2 <- with(dataFile, split(steps,date))
s1 <- lapply(d2,sum, na.rm = T)
s2 <- unsplit(value = s1,f = dataFile$date)

hist(s2,xlab="per day")
```

mean and median of the steps in each day is:

```{r}
(matrix(c(meann <- lapply(d2,mean,na.rm=TRUE),mediann <- lapply(d2,median,na.rm=TRUE)), ncol = 2))
```

## What is the average daily activity pattern?
```{r}
ss <- aggregate(x = dataFile, by = list(dataFile$date,dataFile$interval), FUN = mean, na.rm = T)
plot(ss$interval,ss$steps,type = "l")
```

## Imputing missing values
1- We have
```{r}
nas <- dataFile[which(is.na(dataFile$steps)),]
nrow(nas)
```

Nas in dataset.

2- For imputing missing values, we decided to replace NAs with the mean of the number of steps in that day.
```{r}
imputeNAs <- function(d_item, name){
        mean_steps <- ifelse(is.nan(meann[[name]]), 0, meann[[name]])
        d_item <- ifelse(is.na(d_item), mean_steps, d_item)
}

d4 <- list()
for (name in names(d2)){
        d4 <<- rbind(d4,name = lapply(d2[name],imputeNAs , name))
}

```

3 - Now create a new dataset from imputed values:
```{r}
imp_sum <- lapply(d2,sum)
imputed_final <- unsplit(imp_sum,f = dataFile$date)

```

4- Make a histogram of new dataset:
```{r}
hist(imputed_final)
```

## Are there differences in activity patterns between weekdays and weekends?

In this part I decided to remove all data that both date and steps are NAs. Because they don't give any information and they ruin the analysis. Maybe there is a better way but ....!

```{r}
q <- data.frame(steps = unsplit(d4, dataFile$date))
q$interval <- dataFile$interval
q$date <- dataFile$date

```


1- Create a new factor variable indicating weekday or weekend
```{r}
q <- q[which(!is.na(q$date)),]
q$daytype <- 'weekday'
q[which(weekdays(q$date) %in% c('Saturday','Sunday')),'daytype'] <- 'weekend'
```

2- Make the plot:
```{r}
q1 <- with(q, split(steps,daytype))
subq1 <- subset(q,subset = daytype == 'weekday', select = c("steps","date","interval"))
ssq1 <- aggregate(x = subq1, by = list(subq1$date,subq1$interval), FUN = mean)
plot(ssq1$interval,ssq1$steps,type = "l", xlab = "interval", ylab = "amount of steps")

subq2 <- subset(q,subset = daytype == 'weekend', select = c("steps","date","interval"))
ssq2 <- aggregate(x = subq2, by = list(subq2$date,subq2$interval), FUN = mean)
plot(ssq2$interval,ssq2$steps,type = "l", xlab = "interval", ylab = "amount of steps")

```